Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-02-10 Report/convergence_centralized.tex
additions

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{x}}
\newcommand{\my}{\mbf{y}}
\newcommand{\mz}{\mbf{z}}
\newcommand{\mxb}{{{\mbf{x}}}}
\newcommand{\myb}{{{\mbf{y}}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}
\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

>>>>

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{x}}
\newcommand{\my}{\mbf{y}}
\newcommand{\mz}{\mbf{z}}
\newcommand{\mxb}{{{\mbf{x}}}}
\newcommand{\myb}{{{\mbf{y}}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}
\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}

In order to prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, we have to show the following conditions are to be satisfied.
\begin{itemize}
	\item At each \ac{SCA} update, the objective value decreases monotonically, 
	\item each \ac{SCA} point is unique, which is required for \ac{AO} to converge,
	\item and the objective function is monotonically decreasing at each \ac{AO} update.
\end{itemize}
In addition, we need to show the converged point is the stationary point for the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.

Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

### 2015-02-10 Report/dual_approach.tex
additions

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using subgradient to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
\label{dual-sg-update}
\end{equation}
where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}. The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

>>>>

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using subgradient to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
\label{dual-sg-update}
\end{equation}
where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}, which depend on the system model under consideration for the convergence rate.  The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

### 2015-02-10 Report/kkt_mse_approach.tex
nothing great
additions

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations. The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements. \review{We consider a \ac{TDD} system due to the unquantized channel state information at the transmitter}.  Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. Since the formulation in \cite{kaleva2013decentralized,kaleva2013primal} are similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

@@

To avoid the back-haul exchanges between \acp{BS}, as an alternative approach, users may perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users. Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}. The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders. On receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}. Finally, Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}, \tilde{\epsilon}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
 \ForEach{\ac{BS} \me{b \in \mc{B}}}{
 initialize \me{i = 0} \;
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
	update \me{\mvec{m}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
	find \me{\mvec{w}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{w}{l,k,n}^{(i)}} \;
	using precoded uplink pilots, \me{\mvec{m}{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
	\me{i = i + 1} \;
 }
 }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
 \label{algo-4}
\end{algorithm}\vspace{-0.1in}

The Algorithm \ref{algo-4} outlines a practical approach of implementing the precoder design in a distributed manner using \ac{OTA} signaling of transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed. Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha}, it is difficult to prove the convergence of the algorithm to the centralized point. If the step size \me{\rho < 1}, the algorithm will converge by following the arguments made for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration. Note that the objective is nonincreasing but the queue devation is not.

>>>>

In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}. In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations. The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements. \review{We consider an idealistic assumption of a \ac{TDD} system due to the knowledge of complete channel information at the transmitter}.  Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}. Since the formulation in \cite{kaleva2013decentralized,kaleva2013primal} are similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.

@@

To avoid the back-haul exchanges between \acp{BS}, as an alternative approach, users may perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users. Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}. The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders. On receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}. Finally, Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}, \tilde{\epsilon}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
 \ForEach{\ac{BS} \me{b \in \mc{B}}}{
 initialize \me{i = 0} \;
 \Repeat{until convergence or \me{i \geq I_{\max}}}{
	update \me{\mvec{m}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
	find \me{\mvec{w}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{w}{l,k,n}^{(i)}} \;
	using precoded uplink pilots, \me{\mvec{m}{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
	\me{i = i + 1} \;
 }
 }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
 \label{algo-4}
\end{algorithm}

\review{The Algorithm \ref{algo-4} outlines a practical way of implementing the transmit precoders in a distributed manner using \ac{OTA} signaling of the transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed with it. Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of the centralized problem. Since the problem solution in \eqref{kkt-mse-4} is equivalent to the centralized formulation in \eqref{eqn-mse-2} if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}, the problem is guaranteed to converge to the centralized solution. Note that it requires four iterations to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders. In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations. If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration.}
